Mealtime conversations between parents and their 2-year-old children in five cultural contexts

### 2023-07-12 manuscript/paper.tex
update repo for revision

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction\newline\indent Word count: 7960}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Mealtime conversations between parents and their 2-year-old children in five cultural contexts},
  pdfauthor={Manuel Bohn1, Wilson Filipe da Silva Vieira1, Marta Giner Torréns2, Joscha Kärtner2, Shoji Itakura3, Lilia Cavalcante4, Daniel Haun1, Moritz Köster5,*, \& Patricia Kanngiesser6,*},
  pdflang={en-EN},
  pdfkeywords={Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Mealtime conversations between parents and their 2-year-old children in five cultural contexts}
\author{Manuel Bohn\textsuperscript{1}, Wilson Filipe da Silva Vieira\textsuperscript{1}, Marta Giner Torréns\textsuperscript{2}, Joscha Kärtner\textsuperscript{2}, Shoji Itakura\textsuperscript{3}, Lilia Cavalcante\textsuperscript{4}, Daniel Haun\textsuperscript{1}, Moritz Köster\textsuperscript{5,*}, \& Patricia Kanngiesser\textsuperscript{6,*}}
\date{}

@@

This research was funded by a grant from Volkswagen Foundation (89611--2), awarded to P.K.. The data assessment in Kyoto was partly funded by a JSPS Fellowship to M.K.. We would like to thank all the research assistants who supported the data assessments and coding: Phileas Heim, Chisato Fukuda, Julia Ohlendorf, Marlene Abromeit. We are grateful to Luke Maurits for statistical advice. All data and analysis code can be found in the following repository: \url{https://github.com/ccp-eva/mealtime}.

The authors made the following contributions. Manuel Bohn: Conceptualization, Methodology, Formal Analysis, Visualization, Writing -- original draft, Writing -- review \& editing; Wilson Filipe da Silva Vieira: Investigation, Writing -- review \& editing; Marta Giner Torréns: Investigation, Conceptualization, Methodology, Writing -- review \& editing; Joscha Kärtner: Investigation, Conceptualization, Methodology, Writing -- review \& editing; Shoji Itakura: Investigation, Writing -- review \& editing; Lilia Cavalcante: Investigation, Writing -- review \& editing; Daniel Haun: Investigation, Writing -- review \& editing; Moritz Köster: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Patricia Kanngiesser: Conceptualization, Methodology, Investigation, Writing -- review \& editing.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Department of Psychology, University of Münster, Münster, Germany\\\textsuperscript{3} Doshisha University, Center for Baby Science, Kyoto, Japan\\\textsuperscript{4} Department of Behavior Theory and Research, Federal University of Pará, Belém, Brazil\\\textsuperscript{5} University of Regensburg, Institute of Psychology, Regensburg, Germany\\\textsuperscript{6} University of Plymouth, School of Psychology, Plymouth, UK\\\textsuperscript{*} joint senior author}

\abstract{%
Children all over the world learn language, yet, the contexts in which they do so varies substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, speech acts, themes). We found a comparable pattern of communicative interactions across cultural settings, which were attenuated in ways that likely reflect local norms and values. These results suggest that children encounter similarly structured communicative environments across diverse cultural contexts and will inform theories of language learning.
}

@@

In recent decades, research on language acquisition has focused, to a large extent, on variation in language input and, in particular, the number of words children hear in naturalistic settings. This line of work was sparked by the finding that children who receive more input -- especially speech directly addressing them -- have better language skills (Bang, Bohn, Ramirez, Marchman, \& Fernald, 2022; Hart \& Risley, 1995; Huttenlocher, Haight, Bryk, Seltzer, \& Lyons, 1991; Shneidman \& Goldin-Meadow, 2012; Walker, Greenwood, Hart, \& Carta, 1994; Weisleder \& Fernald, 2013). From a theoretical perspective, more language input increases children's opportunities for learning word-meaning mappings and allows them to build a larger vocabulary (Jones \& Rowland, 2017; Kachergis, Marchman, \& Frank, 2022; McMurray, Horst, \& Samuelson, 2012). The introduction of daylong audio recording devices and automated coding algorithms has provided further momentum to this endeavor (Cristia et al., 2021; Greenwood, Thiemann-Bourque, Walker, Buzhardt, \& Gilkerson, 2011; Lavechin, Bousbib, Bredin, Dupoux, \& Cristia, 2020). As a consequence, the quantity of direct language input plays a central role in theories and formal models of language learning (Braginsky, Yurovsky, Marchman, \& Frank, 2019; Goodman, Dale, \& Li, 2008; Kachergis et al., 2022; Swingley \& Humphrey, 2018).

However, like most of developmental psychology (Amir \& McAuliffe, 2020; Nielsen, Haun, Kärtner, \& Legare, 2017), research on language acquisition has largely focused on affluent societies of the global north and, as a consequence, the resulting theoretical proposals may fail to generalize to other cultural contexts. As studies in a greater variety of cultural settings have begun to accumulate (Altınkamış, Kern, \& Sofu, 2014; Bergelson et al., 2019; Bunce et al., 2020; Casillas, Brown, \& Levinson, 2021; Choi, 2000; Cristia, Dupoux, Gurven, \& Stieglitz, 2019; Loukatou, Scaff, Demuth, Cristia, \& Havron, 2021; Tardif, Shatz, \& Naigles, 1997), they have revealed substantial cultural variation in how much direct input children receive (Cristia, 2022; see also Sperry, Sperry, \& Miller, 2019 for variation within an English-speaking sample). Yet, children still reach major milestones in language development at similar ages (Brown \& Gaskins, 2014; Casillas, Brown, \& Levinson, 2020). These findings highlight that theories and models of language learning need to extend beyond quantity of input and also include learning processes that compensate for variation in input (Bang, Mora, Munévar, Fernald, \& Marchman, 2022; Casillas, 2022; Jones \& Rowland, 2017; Kachergis et al., 2022; Meylan \& Bergelson, 2022).

It has been suggested that these compensatory learning processes leverage structural features of social interactions in which language is used (Casillas et al., 2020; Rogoff, Paradise, Arauz, Correa-Chávez, \& Angelillo, 2003; Shneidman \& Goldin-Meadow, 2012; Shneidman \& Woodward, 2016). Pragmatic accounts of language learning offer an explanation for how children use contextual information (e.g., Bohn \& Frank, 2019; Tomasello, 2009): Social interactions, especially routines, follow predictable patterns that make it easier for children to infer what speakers are communicating about (Barbaro \& Fausey, 2022; Lieven, 1994; Masek, Ramirez, McMillan, Hirsh-Pasek, \& Golinkoff, 2021). For instance, Roy, Frank, DeCamp, Miller, and Roy (2015) found that words were more easily learned when they were primarily used in a distinct spatial and temporal context. Similarly, establishing common ground over the course of an interaction provides information about the speaker's intention independent of the words that are being used (Bohn \& Köymen, 2018; Bohn, Tessler, Merrick, \& Frank, 2021). For example, Bohn, Le, Peloquin, Köymen, and Frank (2021) showed that children identify the referent of an ambiguous word by inferring the topic of an ongoing conversation (see also Akhtar, 2002). These findings help to explain why the amount of conversational turn-taking in parent-child interactions predicts child language outcomes (Donnelly \& Kidd, 2021; Romeo et al., 2018). Turn-taking results in continuous, structured conversations that provide information-rich learning opportunities.

In order to assess whether children can use structural features to complement direct verbal input, it is crucial to compare communicative interactions between adults and children across cultural settings. However, to our knowledge, there are very few quantitative comparisons. While ethnographic descriptions offer important and rich insights into individual cultural settings (see e.g., De León, 2011; Gaskins, 2006), quantitative comparisons are essential for understanding gradual cultural differences (Broesch et al., 2021; Hewlett, Lamb, Shannon, Leyendecker, \& Schölmerich, 1998; Köster et al., 2022) and offer core input for theory building (see language input studies discussed earlier).

One of the challenges of cross-cultural work lies in selecting an appropriate context for comparing the structure of communicative interactions (Broesch, Lew-Levy, Kärtner, Kanngiesser, \& Kline, 2022). Prior work has shown that the amount of language input children receive varies substantially across routine activities. For example, Soderstrom and Wittebolle (2013) found that Canadian adults spoke most during book reading and structured playtime (see also Tamis-LeMonda, Custode, Kuchirko, Escobar, \& Lo, 2019). Such activities, however, are very specific to industrialized societies and less frequent or absent in other cultural contexts. A cross-culturally recurrent, and hence particularly promising, context for cross-cultural research is mealtime: across societies, meals are social events that are structured by -- and used to transmit -- cultural norms, values and beliefs (Blum-Kulka, 2012; Fjellström, 2004; Köster et al., 2022; Ochs \& Shohet, 2006). Furthermore, mealtimes have been a fruitful context for studying caregiver-child communication, for example, in the U.S. (e.g., Beals, 1993, 1997; Snow \& Beals, 2006).

@@

The goal of this study was to compare communicative interactions between parents and their children during mealtime across diverse cultural settings. We aimed for a naturalistic but comparable setup by a) asking families to record in their homes, b) recruiting families with a single -- usually the first -- child between 2 and 3 years of age and c) focusing on 10-minute-long episodes during which three family members (mother, father, one child) were present. Even though the constellation of two parents and one child might be less representative of the overall family demographics in some settings, it allowed us to directly quantify and compare communicative interactions. We obtained recordings from five different cultural settings, including families living in the Global South and North, as well as in urban and rural settings: the city of Buenos Aires, Argentina, small villages in the Apeú region, Brazil, small villages close to Cotacachi, Ecuador, the city of Münster, Germany, and the city of Kyoto, Japan.

We coded and analyzed the data along nine dimensions that focused on the quantity of talk and gestures as well as their conversational embedding (interlocutors, speech acts, themes). In a first step, we analyzed if and how these dimensions differed in the five cultural settings. In a second step, we asked whether some cultural settings are more similar to one another. The five cultural settings offer an interesting perspective on the factors influencing mealtime conversations. For example, communicative interaction patterns could cluster by country (five clusters; one cluster per country), or by language family and geographical region (three clusters; Argentina, Brazil, Ecuador vs.~Germany vs.~Japan) or by degree of urbanization (two clusters; urban: Argentina, Germany, Japan vs.~rural: Brazil, Ecuador). Based on previous work, we expected less direct input to children in the rural contexts (Cristia, 2022) but -- given a lack of comparable previous work -- we had no specific predictions for variation in the structure of communicative interactions.

@@

Here we coded who produced the utterance. The speaker could either be \texttt{child}, \texttt{mother}, or \texttt{father}. All sections containing no speech were coded as \texttt{silence}.

@@

\hypertarget{themes-and-rounds}{%
\subsubsection{Themes and rounds}\label{themes-and-rounds}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction\newline\indent Word count: 8454}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Mealtime conversations between parents and their 2-year-old children in five cultural contexts},
  pdfauthor={Manuel Bohn1,2, Wilson Filipe da Silva Vieira2, Marta Giner Torréns3, Joscha Kärtner3, Shoji Itakura4, Lília Cavalcante5, Daniel Haun2, Moritz Köster6,*, \& Patricia Kanngiesser7,*},
  pdflang={en-EN},
  pdfkeywords={Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Mealtime conversations between parents and their 2-year-old children in five cultural contexts}
\author{Manuel Bohn\textsuperscript{1,2}, Wilson Filipe da Silva Vieira\textsuperscript{2}, Marta Giner Torréns\textsuperscript{3}, Joscha Kärtner\textsuperscript{3}, Shoji Itakura\textsuperscript{4}, Lília Cavalcante\textsuperscript{5}, Daniel Haun\textsuperscript{2}, Moritz Köster\textsuperscript{6,*}, \& Patricia Kanngiesser\textsuperscript{7,*}}
\date{}

@@

This research was funded by a grant from Volkswagen Foundation (89611--2), awarded to P.K.. The data assessment in Kyoto was partly funded by a JSPS Fellowship to M.K.. M.B. was supported by a Jacobs Foundation Research Fellowship. We would like to thank all the research assistants who supported the data assessments and coding: Phileas Heim, Chisato Fukuda, Julia Ohlendorf, Marlene Abromeit. We are grateful to Luke Maurits for statistical advice. All data and analysis code can be found in the following repository: \url{https://github.com/ccp-eva/mealtime}.

The authors made the following contributions. Manuel Bohn: Conceptualization, Methodology, Formal Analysis, Visualization, Writing -- original draft, Writing -- review \& editing; Wilson Filipe da Silva Vieira: Investigation, Writing -- review \& editing; Marta Giner Torréns: Investigation, Conceptualization, Methodology, Writing -- review \& editing; Joscha Kärtner: Investigation, Conceptualization, Methodology, Writing -- review \& editing; Shoji Itakura: Investigation, Writing -- review \& editing; Lília Cavalcante: Investigation, Writing -- review \& editing; Daniel Haun: Investigation, Writing -- review \& editing; Moritz Köster: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Patricia Kanngiesser: Conceptualization, Methodology, Investigation, Writing -- review \& editing.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology, Leuphana University Lüneburg, Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{3} Department of Psychology, University of Münster, Münster, Germany\\\textsuperscript{4} Center for Baby Science, Doshisha University, Kyoto, Japan\\\textsuperscript{5} Graduate Program in Theory and Research of Behavior, Federal University of Pará, Belém, Brazil\\\textsuperscript{6} Institute of Psychology, University of Regensburg, Regensburg, Germany\\\textsuperscript{7} School of Psychology, University of Plymouth, Plymouth, UK\\\textsuperscript{*} joint senior authors}

\abstract{%
Children all over the world learn language, yet, the contexts in which they do so varies substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, function, themes). We found a comparable pattern of communicative interactions across cultural settings, which were modified in ways that are consistent with local norms and values. These results suggest that children encounter similarly structured communicative environments across diverse cultural contexts and will inform theories of language learning.
}

@@

In recent decades, research on language acquisition has focused, to a large extent, on variation in language input and, in particular, the number of words children hear in naturalistic settings. This line of work was sparked by the finding that children who receive more input -- especially speech directly addressing them -- have larger vocabularies (Bang, Bohn, Ramirez, Marchman, \& Fernald, 2022; Hart \& Risley, 1995; Huttenlocher, Haight, Bryk, Seltzer, \& Lyons, 1991; Shneidman \& Goldin-Meadow, 2012; Walker, Greenwood, Hart, \& Carta, 1994; Weisleder \& Fernald, 2013). From a theoretical perspective, more language input increases children's opportunities for learning word-meaning mappings and allows them to build a larger vocabulary (Jones \& Rowland, 2017; Kachergis, Marchman, \& Frank, 2022; McMurray, Horst, \& Samuelson, 2012). The introduction of daylong audio recording devices and automated coding algorithms has provided further momentum to this endeavor (Cristia et al., 2021; Greenwood, Thiemann-Bourque, Walker, Buzhardt, \& Gilkerson, 2011; Lavechin, Bousbib, Bredin, Dupoux, \& Cristia, 2020). As a consequence, the quantity of direct language input plays a central role in theories and formal models of language learning (Braginsky, Yurovsky, Marchman, \& Frank, 2019; Goodman, Dale, \& Li, 2008; Kachergis et al., 2022; Swingley \& Humphrey, 2018).

However, like most of developmental psychology (Amir \& McAuliffe, 2020; Nielsen, Haun, Kärtner, \& Legare, 2017), research on language acquisition has largely focused on affluent societies of the Global North and the resulting theoretical proposals may fail to generalize to other cultural contexts. As studies in a greater variety of cultural settings have begun to accumulate (Altınkamış, Kern, \& Sofu, 2014; Bergelson et al., 2019; Bunce et al., 2020; Casillas, Brown, \& Levinson, 2021; Choi, 2000; Cristia, Dupoux, Gurven, \& Stieglitz, 2019; Loukatou, Scaff, Demuth, Cristia, \& Havron, 2021; Tardif, Shatz, \& Naigles, 1997), they have revealed substantial cultural variation in how much direct input children receive (Cristia, 2022; see also Sperry, Sperry, \& Miller, 2019 for variation within an English-speaking sample). Yet, children still reach major milestones in language development at similar ages (Brown \& Gaskins, 2014; Casillas, Brown, \& Levinson, 2020). These findings highlight that theories and models of language learning need to extend beyond quantity of input and also include learning processes that compensate for variation in input (Bang, Mora, Munévar, Fernald, \& Marchman, 2022; Casillas, 2022; Jones \& Rowland, 2017; Kachergis et al., 2022; Meylan \& Bergelson, 2022).

It has been suggested that these compensatory learning processes leverage structural features of social interactions in which language is used (Casillas et al., 2020; Rogoff, Paradise, Arauz, Correa-Chávez, \& Angelillo, 2003; Shneidman \& Goldin-Meadow, 2012; Shneidman \& Woodward, 2016). Pragmatic accounts of language learning offer an explanation for how children use contextual information (e.g., Bohn \& Frank, 2019; Tomasello, 2009): Social interactions, especially routines, follow predictable patterns that make it easier for children to infer what speakers are communicating about (Barbaro \& Fausey, 2022; Bruner, 1983; Lieven, 1994; Masek, Ramirez, McMillan, Hirsh-Pasek, \& Golinkoff, 2021; Vygotsky, 1978). For instance, Roy, Frank, DeCamp, Miller, and Roy (2015) found that words were more easily learned when they were primarily used in a distinct spatial and temporal context. Similarly, establishing common ground over the course of an interaction provides information about the speaker's intention independent of the words that are being used (Bohn \& Köymen, 2018; Bohn, Tessler, Merrick, \& Frank, 2021). For example, Bohn, Le, Peloquin, Köymen, and Frank (2021) showed that children identify the referent of an ambiguous word by inferring the topic of an ongoing conversation (see also Akhtar, 2002). These findings help to explain why the amount of conversational turn-taking in parent-child interactions predicts child language outcomes (Donnelly \& Kidd, 2021; Romeo et al., 2018). Turn-taking results in continuous, structured conversations that provide information-rich learning opportunities.

To assess whether children can use structural features to complement direct verbal input, it is crucial to compare communicative interactions between adults and children across cultural settings. However, to our knowledge, there are very few quantitative comparisons. While ethnographic descriptions offer important and rich insights into individual cultural settings (see e.g., De León, 2011; Gaskins, 2006), quantitative comparisons are essential for understanding gradual cultural differences (Broesch et al., 2021; Hewlett, Lamb, Shannon, Leyendecker, \& Schölmerich, 1998; Köster et al., 2022) and offer core input for theory building.

One of the challenges of cross-cultural work lies in selecting an appropriate context for comparing the structure of communicative interactions (Broesch, Lew-Levy, Kärtner, Kanngiesser, \& Kline, 2022). Prior work has shown that the amount of language input children receive varies substantially across routine activities. For example, Soderstrom and Wittebolle (2013) found that Canadian adults spoke most during book reading and structured playtime (see also Tamis-LeMonda, Custode, Kuchirko, Escobar, \& Lo, 2019). Such activities, however, are very specific to industrialized societies and less frequent or absent in other cultural contexts. A cross-culturally recurrent, and hence particularly promising, context for cross-cultural research are mealtimes: across societies, meals are social events that are structured by -- and used to transmit -- cultural norms, values and beliefs (Blum-Kulka, 2012; Fjellström, 2004; Köster et al., 2022; Ochs \& Shohet, 2006). Furthermore, mealtimes have proven fruitful for studying caregiver-child communication in cultural contexts like the U.S. (e.g., Beals, 1993, 1997; Snow \& Beals, 2006).

@@

The goal of this study was to compare communicative interactions between parents and their children during mealtimes across diverse cultural settings. We aimed for a naturalistic but comparable setup by a) asking families to record in their homes, b) recruiting families with a single -- usually the first -- child between 2 and 3 years of age and c) focusing on 10-minute-long episodes during which three family members (mother, father, one child) were present. Even though the constellation of two parents and one child might be less representative of the overall family demographics in some settings, it allowed us to directly quantify and compare communicative interactions.

We obtained recordings from five different cultural settings, including families living in the Global South and the Global North, as well as in urban and rural settings: the city of Buenos Aires in Argentina, small villages in the Amazon region near Apeú in Brazil), small villages close to Cotacachi in Ecuador, the city of Münster in Germany, and the city of Kyoto in Japan. This sample was first and foremost a convenience sample of families in diverse cultural settings we had worked with previously. This continues to be a common approach in larger-scale cross-cultural, developmental studies (P. R. Blake et al., 2015; House et al., 2020, 2013; Kanngiesser et al., 2022) and is often the first step when little substantive cross-cultural data exists to inform targeted comparisons. Nevertheless, in addition to their geographic spread and variation in population density, the settings also varied in cultural norms and beliefs about communication during mealtimes. In Germany, meals are seen as a privileged time for communication and exchange (Danesi, 2018). Similarly, in Argentina, dinners are an important opportunity for family conversations because it is usually the only time when the whole family gets together (Aguirre, 2016). In contrast, within the Kichwa indigenous people in Ecuador meals are supposed to be taken in silence (Sánchez-Parga, 2010). In Japan, both views are common and whether or not talk is encouraged depends, in part, on the eating arrangements (Imada \& Furumitsu, 2020). As such, our sample provided us with the opportunity to study if and how different cultural mealtime norms impact real-world communicative interactions.

We coded and analyzed our video data along several dimensions, focusing on the quantity of talk and gestures as well as their conversational embedding . We chose dimensions that have been implicated as relevant for child language acquisition, but have rarely been studied from a cross-cultural perspective. First, we coded the presence (or absence) of speech, the identity of the speaker and the recipient. This allowed us to quantify how much directed talk -- as opposed to overheard talk -- children received and from whom. As noted above, cross-cultural variation in talk directed at the child has profound theoretical implications because it questions the privileged role given to direct input in many theoretical accounts of language learning. Coding speaker identity provided insight into who children receive language input from. Cross-cultural research on different sources of language input is relatively scarce: most past studies have exclusively focused on maternal talk and only recently have researchers begun to investigate paternal talk (Ferjan Ramírez, 2022). By coding the language produced by children themselves, we were able to quantify children's role in shaping their linguistic environment across cultural contexts (Donnellan, Bannard, McGillion, Slocombe, \& Matthews, 2020; Tamis-LeMonda, Kuchirko, \& Suh, 2018). In addition to speech, we also coded the production of gestures. A substantial body of research has shown that gestures produced by children and their caregivers relate to child language competency -- at least in children growing up in the Global North (Colonnesi, Stams, Koster, \& Noom, 2010; e.g., Rowe, Özçalışkan, \& Goldin-Meadow, 2008). Here, the view is that gestures act as a complementary source of input that reference objects and events in the environment and thereby facilitate word learning (Tomasello, 2005).

Second, we coded how utterances were grouped into themes. This approach allowed us to quantify cross-cultural variation in how conversations are structured. Research on conversational turn-taking has suggested a link between these structural features and language learning (Donnelly \& Kidd, 2021; Romeo et al., 2018); yet, a cross cultural perspective is still largely missing. Finally, we coded the function of utterances and distinguished between questions, assertions and imperatives. Questions play a role in facilitating language acquisition because they encourage verbal responses from children which may include labels for objects (J. Blake, Macdonald, Bayrami, Agosta, \& Milian, 2006). There is also suggestive evidence of cultural variation in how parents use functional elements of language such as questions (Kuchirko, Schatz, Fletcher, \& Tamis-Lemonda, 2020).

For the analysis, we first assessed if and how these coded dimensions differed in the five cultural settings. In a second step, we asked whether some cultural settings are more similar to one another. The five cultural settings offer an interesting perspective on the factors influencing mealtime conversations. For example, communicative interaction patterns could cluster by country (five clusters; one cluster per country), or by language family and geographical region (three clusters; Argentina, Brazil, Ecuador vs.~Germany vs.~Japan) or by degree of urbanization (two clusters; urban: Argentina, Germany, Japan vs.~rural: Brazil, Ecuador). Based on previous work, we expected less direct input to children in the rural contexts (Cristia, 2022). Due to different cultural norms around mealtime conversations, we predicted less overall talk in Ecuador compared to Germany, with Japan falling somewhere in the middle. Given a lack of comparable previous work -- we had no specific predictions for variation in the structure of communicative interactions.

@@

Here we coded who produced the utterance. The speaker could either be \texttt{child}, \texttt{mother}, or \texttt{father}. All sections containing no speech were coded as \texttt{non-talk}.

@@

\hypertarget{themes-and-utterances}{%
\subsubsection{Themes and utterances}\label{themes-and-utterances}}
